---
title: "Change GitHub filenames to Databrary format"
author: "Rick O. Gilmore"
date: "February 15, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Planning our work

- Download spreadsheet with all names. `databraryandbox-Gilmore-child-motion-form.xls` from Google Drive.
- Change all files in `analysis/data/csv-bysession` from `YYYYMMDD_HHMMSS.csv` to the following format: `<databrary-session-id>-<databrary-participant-id>.csv`
    - Load spreadsheet
    - For each row, find the value in column `Github`, create a filename from that value by adding `.csv`
    - Find this filename in `analysis/data/csv-bysession`
    - If we find it, change it to `<session-id>-<participant-ID>.csv`
    
## Open spreadsheet

```{r open-ss}
db.ss <- read.csv(file = "analysis/data/databraryandbox-Gilmore-child-motion-form .xls - databrary144-Gilmore-child-moti.csv", header = TRUE)
```

Let's try opening one line as an experiment.

```{r open-1-line}
fn <- paste(db.ss[1,'Github'], ".csv", sep="")
new.fn <- paste(db.ss[1, 'session.id'], "-", db.ss[1,'participant.ID'], ".csv", sep="")
fn <- paste("analysis/data/csv-bysession/", fn, sep="")
new.fn <- paste("analysis/data/csv-bysession/", new.fn, sep="")
if (file.exists(fn)) {
  file.rename(from = fn, to=new.fn)
}
```
A smarter way to do this would be to write a function and apply it across all of the files.

```{r change-name-function}
Rename.mofo.files <- function(row, db, data.dir="analysis/data/csv-bysession/") {
  # Take rows of db file and rename
  # Parameters
  #   row: row number in the db spreadsheet
  #   db: dataframe imported from csv file
  #   data.dir: director for session data files
  
  fn <- paste(data.dir, db[row,'Github'], ".csv", sep="")
  new.fn <- paste(data.dir, db[row, 'session.id'], "-", db[row,'participant.ID'], ".csv", sep="")
  if (file.exists(fn)) {
    file.rename(from = fn, to = new.fn)
    message(sprintf("Renamed %s to %s.", fn, new.fn))
  } else {
    warning(sprintf("%s does not exist.", fn))
  }
}
```

This function seems to work. Hooray!

Now, let's list-ify it.

```{r run-function-over-list}
lapply(1:length(list.files("analysis/data/csv-bysession/")), Rename.mofo.files, db=db.ss)
```